An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-18 indicators/paper/paper.tex
Copyedits to discussion

Auxiliary signals (outside of the standard public health reporting streams) can
serve as indicators of COVID activity, but they can illustrate the effect of
mitigating actions (such as shelter-in-place orders) and can guide resource
allocation for fighting the pandemic. For example, medical claims data reflects
healthcare-seeking behavior; measures of mobility reflect adherence to public
health recommendations; and measures of COVID vaccine acceptance can guide
outreach efforts.

@@

Finally, we emphasize that unifying many relevant signals into a single common
format, with comprehensive revision tracking, is a valuable goal in and of
itself. The ability to combine public health reporting data, syndromic
surveillance data, and digital surveillance measures of mobility and behaviors
creates a platform that goes beyond providing situational awareness. Providing
convenient and real-time access to this data provides continuous telemetry
summarizing how things are, how they are expected to change, which areas need
additional resources to be allocated in response, and how effective public
communication is.

>>>>

Auxiliary signals (outside of the standard public health reporting streams) can
serve as indicators of COVID activity, but they can also illustrate the effect
of mitigating actions (such as shelter-in-place orders) and can guide resource 
allocation for fighting the pandemic. For example, medical claims data reflects
healthcare-seeking behavior; measures of mobility reflect adherence to public
health recommendations; and measures of COVID vaccine acceptance can guide
outreach efforts.

@@

Finally, we emphasize that unifying many relevant signals into a single common
format, with comprehensive revision tracking, is an important goal in and of 
itself. The ability to combine public health reporting data, syndromic
surveillance data, and digital measures of mobility and behaviors goes beyond
providing traditional situational awareness.  Convenient and real-time access to
this data enables continuous telemetry summarizing how things are, how they are
expected to change, which areas need additional resources to be allocated in
response, and how effective public communication is.
